%\title{My 2 Columns CV}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right
\privacy

\namesection{Niccolò}{Olivieri Achille}{ % Your name
\urlstyle{same}\url{http://lnkd.in/b9ZrkZq} \\ % Your website, LinkedIn profile or other web address
\href{mailto:niccolo@olivieriachille.com}{niccolo@olivieriachille.com} | 388-6465482 % Your contact information
}

%----------------------------------------------------------------------------------------
%	MAIN COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{1\textwidth}

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Dear Sir or Madam}

I am a web and frontend passionate and discovering that you are searching exactly what I suit for is something incredible.

\vspace{5mm}

Right now I am working as a frontend developer, so things like CSS3, Bootstrap, Ajax and Responsive Design are my bread and butter.

One of the projects I am on uses NodeJS and MongoDB, and I have provided the entire initial structure of it, solving all common issues that we could find once in production (by the way, that project IS in production from late 2013). 

I am also really curious about new features of the language, so I am discovering \textbf{generators} and ``\textbf{Koa}'' to replace old libraries with something more cutting-edge ones.

\vspace{5mm}

PHP has been my ``developing mother tongue'' for almost a decade, I have coded my own MVC framework from scratch (for my first thesis) when I was too young to understand and use third party ones, then I have switched to something more structured as ``\textbf{Zend Framework}'', to abandon it as soon as version 2.0 was released. From that moment I searched for a new framework to work with, explored ``\textbf{Yii}'' and ``\textbf{Symfony}'' to finally land on ``\textbf{Laravel 4.0}'' as soon as it was released.

Later on, both for work and for a sort of evolution process, I gave up frameworks to use ``\textbf{Wordpress}'' in every situation, actually, using that CMS like a framework (or better ecosystem) itself.

\vspace{5mm}

Then I have to be honest, I had something like a heartbreak when I read ``\textbf{highcharts}'': someone is using it after all! I used it all the time I worked for Vodafone, the web application I developed uses that library to visualize all the data we were collecting from various sources. Since then I have not followed its development, but every now and then I enter its website and I cannot see big changes.

\vspace{5mm}

I use \textbf{SCRUM} (even if in a slightly modified version) daily at work and I am a huge fan of it: I tried to introduce it also at home (or at least Kanbam), but my wife did not take it well.

\vspace{5mm}

Last but not least, I introduced ``\textbf{.git}'' as the standard ``de facto'', using it not only for code history, but also to publish on production servers, in a multi-branch environment. Moreover I have thought about our new server infrastructure, introducing a multi-layer clustered concept that was something like a chimera even one year ago.

\vspace{5mm}

New challenges excite me, working in a company that chooses cutting-edge technologies is my dream, so I see your company as the right place to go. I actually think that thanks to my former experience, I can be a great addition to your company and look forward to being interviewed at your earliest convenience.

Thank you for your time and consideration. I look forward to hearing from you.

\vspace{10mm}

Yours faithfully,

\vspace{5mm}

Niccolò Olivieri Achille

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}